\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-06 paper/ms.tex
ABC results plot
Mention postprocess_abc
Change of coordinates

>>>>

In ABC applications the model class needs to describe a point in the joint
(parameters, data) space, and the \code{from\_prior} and \code{perturb}
functions need to respect the joint prior distribution.
In Bayesian inference the joint prior tends to make the
parameters and data highly dependent
--- otherwise the data wouldn't ever be informative about the parameters.
To improve efficiency, it is helpful to use a change of variables such that
the parameters and data-controlling variables are independent. In this
example we use

\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &= \textnormal{Uniform}(-10, 10)\\
n_i &= \textnormal{Normal}(0, 1)
\end{align}
where each of the $n_i$ enables a data point to be calculated using
\begin{align}
x_i &= \mu + \sigma n_i
\end{align}

We show posterior samples in Figure~\ref{fig:abc_results}.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.6\textwidth]{figures/abc_results.pdf}
\caption{ABC results.\label{fig:abc_results}}
\end{figure}

For ABC applications, there is an alternate \code{postprocess()} function:
\begin{CodeChunk}
\begin{CodeInput}
import dnest4.classic as dn4
dn4.postprocess_abc()
\end{CodeInput}
\end{CodeChunk}
